---
title: "demtables"
output: html_document
---

## R Markdown

`demtables` is a simple package for making demographic tables from data.frames.

### Installation

Installation is simplest through `devtools::install_github`. The package depends on `dplyr`, `tidyr`, `htmlTable`, and `formula.tools`.

```{r install, echo = TRUE, eval = FALSE}
devtools::install_github('sean-cho/demtables')
```

### Usage

The main workhorse of the `demtables` package is the function `dem_table` which takes a `data.frame` and `expression` as an argument.

```{r demtable, echo = TRUE}
library(demtables)
library(survival)
data(ovarian)
ovarian %>% 
  mutate(resid.ds = ifelse(resid.ds == 1,'no','yes'), rx = factor(rx)) %>% 
  dem_table(rx ~ .)
```

Alternatively, you could select specific variables.

```{r demtable_sub, echo = TRUE}
ovarian %>% 
  mutate(resid.ds = ifelse(resid.ds == 1,'no','yes'), rx = factor(rx)) %>% 
  dem_table(rx ~ age + resid.ds)
```

The `make_dem_table` and `view_dem_table` functions create HTML tables that will be displayed in the Viewer if you use RStudio. `make_dem_table` can be used directly in HTML Markdowns.

```{r make_demtable, echo = TRUE}
ovarian %>% 
  mutate(resid.ds = ifelse(resid.ds == 1,'no','yes'), rx = factor(rx)) %>% 
  make_dem_table(rx ~ age + resid.ds, 'Ovarian data')
```
